Parallel global optimization algorithm with uniform convergence for solving a set of constrained global optimization problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-06-14 2020/OPTIMA/optima_paper.tex
OPTIMA: fix issues with eps-reserves

Step 4. For all nonempty sets \(I_{\nu },\nu ={\overline {1,M}}\) compute the estimates
\begin{equation}
  \label{eq:step_4}
  z_{\nu }^{*}={\begin{cases}\min\{g_{\nu }(x_{i}):x_{i}\in I_{\nu }\},&\nu =M,\\-\varepsilon
_{\nu },&\nu <M,\end{cases}}
\end{equation}
where the vector with the non-negative coordinates \(\varepsilon _{R}=(\varepsilon
_{1},..,\varepsilon _{m})\) is called the vector of reserves.

@@

Along with GCGen system, the examples of its application and constructing the set of problems
each consisting of an objective function and two constraints generated by \(F_{GR}\)
\cite{grishaginClass} generator or GKLS \cite{Gaviano2003} one Are distributed.
GKLS \cite{Gaviano2003} allows obtaining the functions of predefined dimensionality and
with predefined number of extrema.
In combination with GCGen, two sets of 100 problems each of the dimensionalities 2 and 3
were generated.
Each problem had two constraints.
Also, in order to demonstrate the properties of the method to be preserved at essentially
different properties of the problems, a mixed class consisting of 50 problems with
two-dimensional GKLS functions and 50 problems with \(F_{GR}\) ones was generated.
Examples of contour plots of the considered problems are presented in Fig. \ref{fig:isolines}.
The feasible domain is highlighted by color.

@@

The results of solving the test problems by the sequential and parallel versions of the modified
IAGS for solving the sets of problems are presented in Table~\ref{tab:speedup}.
For all two-dimensional classes of problems, the parameter \(r=4.7\).
In the case of the three-dimensional problems, \(r=4.7,\: \varepsilon_\nu=0.1\).
In all experiments, an additional computational load was introduced into the objective function
and constraints so that the time of a single call of a problem function was equal to
approximately 1 ms.

>>>>

Step 4. For all nonempty sets \(I_{\nu },\nu ={\overline {1,M}}\) compute the estimates
\begin{equation}
  \label{eq:step_4}
  z_{\nu }^{*}={\begin{cases}\min\{g_{\nu }(x_{i}):x_{i}\in I_{\nu }\},&\nu =M,\\
  0,&\nu <M,\end{cases}}.
\end{equation}

@@

Along with GCGen system, the examples of its application and constructing the set of problems
each consisting of an objective function and two constraints generated by \(F_{GR}\)
\cite{grishaginClass} generator or GKLS \cite{Gaviano2003} one Are distributed.
GKLS \cite{Gaviano2003} allows obtaining the functions of predefined dimensionality and
with predefined number of global optimums.
In combination with GCGen, two sets of 100 problems each of the dimensionalities 2 and 3
were generated.
Each problem had two constraints.
Also, in order to demonstrate the properties of the method to be preserved at essentially
different properties of the problems, a mixed class consisting of 50 problems with
two-dimensional GKLS functions and 50 problems with \(F_{GR}\) ones was generated.
Examples of contour plots of the considered problems are presented in Fig. \ref{fig:isolines}.
The feasible domain is highlighted by color.

@@

The results of solving the test problems by the sequential and parallel versions of the modified
IAGS for solving the sets of problems are presented in Table~\ref{tab:speedup}.
For all two-dimensional classes of problems, the parameter \(r=4.7\).
In the case of the three-dimensional problems, \(r=4.7\) and also to improve the convergence speed
\(\varepsilon\)-reservation technique from \cite{Strongin2000} Chapter 8.3 with
\(\varepsilon=0.1\) has been employed.
In all experiments, an additional computational load was introduced into the objective function
and constraints so that the time of a single call of a problem function was equal to
approximately 1 ms.
